Simulation of seed dispersal distance - 10 runs

### 2020-10-12 appendixB/sim10/appendixB_10.Rmd
arranged all tables according to ldd n

```{r}
seed_data_popind %>% 
  mutate(type = ifelse(data == "POP", "POP", "IND")) %>% 
  bind_rows(., mixed_ind) %>% 
  mutate(., LDD = ifelse(dispersal >= 500, 1, 0)) %>% 
  group_by(type, dist) %>% 
  summarise(n = n(),
            mean_disp = mean(dispersal),
            max_disp = max(dispersal), 
            n_ldd = sum(LDD),
            prcnt_ldd = n_ldd/n) %>% 
  knitr::kable()

@@

Family level
```{r}
seed_data_popfam %>% 
  mutate(type = ifelse(data == "POP", "POP", "FAM")) %>% 
  bind_rows(., mixed_fam) %>% 
  mutate(., LDD = ifelse(dispersal >= 500, 1, 0)) %>% 
  group_by(type, dist) %>% 
  summarise(n = n(),
            mean_disp = mean(dispersal),
            max_disp = max(dispersal), 
            n_ldd = sum(LDD),
            prcnt_ldd = n_ldd/n) %>% 
  knitr::kable()
```

>>>>

```{r}
seed_data_popind %>% 
  mutate(type = ifelse(data == "POP", "POP", "IND")) %>% 
  bind_rows(., mixed_ind) %>% 
  mutate(., LDD = ifelse(dispersal >= 500, 1, 0)) %>% 
  group_by(type, dist) %>% 
  summarise(n = n(),
            mean_disp = mean(dispersal),
            max_disp = max(dispersal), 
            n_ldd = sum(LDD),
            prcnt_ldd = n_ldd/n) %>% 
  arrange(., desc(prcnt_ldd)) %>% 
  knitr::kable()

@@

Family level
```{r}
seed_data_popfam %>% 
  mutate(type = ifelse(data == "POP", "POP", "FAM")) %>% 
  bind_rows(., mixed_fam) %>% 
  mutate(., LDD = ifelse(dispersal >= 500, 1, 0)) %>% 
  group_by(type, dist) %>% 
  summarise(n = n(),
            mean_disp = mean(dispersal),
            max_disp = max(dispersal), 
            n_ldd = sum(LDD),
            prcnt_ldd = n_ldd/n) %>% 
  arrange(., desc(prcnt_ldd)) %>% 
  knitr::kable()
```
